---
title: 'QM Assignment #3'
output:
  word_document: default
  html_document: default
  pdf_document: default
---
getwd()

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1 Solve the problem using lpsolve, or any other equivalent library in R.
```{r}
library(lpSolve)
library(lpSolveAPI)
lprec <- read.lp("QM#2Solution.lp")
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
X <- "QM#2Solution.lp"
```

# 2 Identify the shadow prices, dual solution, and reduced costs
```{r}
#Get shadow prices
get.sensitivity.rhs(lprec)
#Get dual solution 
get.dual.solution(lprec)
#Get reduced costs 
get.sensitivity.obj(lprec)

```


#3 identify the sensitivity of the above prices and costs. That is, specify the range of shadow prices and reduced cost within which the optimal solution will not change.
```{r}
# The range of the shadow prices within the optimal solution that will not change are the valid ranges of -1.000000e+30 to 5.181818e+03. The shadow price for constraint one to three is zero. The range of reduced costs is -1.00e+30 to 4.60e+.02 . 

```


#4 Formulate the dual of the above problem and solve it. Does the solution agree with what you observed for the primal problem?
```{r}
library(lpSolveAPI)
library(lpSolve)
lprec <- read.lp("3RSTUDIO.lp")
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
Y <- "QM#2Solution.lp"
```

#this solution somewhat agrees with what I observed in the orignal primal problem. When I orignially solved the primal problem, I got 696,000. When I solved the duality function, I got 698,000.4. The reason why they are 2,000.2 apart is due to the additional Y10 and Y11 constraints. This is why there is a price difference. 