---
title: 'QMM Assignment #5'
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Benchmarking)
library(lpSolveAPI)
library(ucminf)
library(quadprog)
```

#1) Formulate and perform DEA analysis under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH. 
```{r}
# Using Benchmarking Libraries for DEA
library(Benchmarking)
library(lpSolveAPI)
library(ucminf)
library(quadprog)
X <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2.0,1.2,.7), ncol=2)
Y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)

colnames(X) <- c("TP", "RP")
colnames(Y) <- c("Staffing Labor Per Hour", "Cost of Supplies per day")
X
Y

#DEA Analysis 

e <- dea(X,Y,RTS = "crs")            # provide the input and output 
e
peers(e)                             # identify the peers
lambda(e)                            # identify the relative weights given to the peers
dea.plot.isoquant(x,y,RTS="crs")     # plot the results

#FDH Assumptions

FDH <- dea (X,Y, RTS = "fdh")
FDH

peers(FDH)
lambda(FDH)
dea.plot.frontier(X,Y,RTS="FDH")
summary(FDH, digits=4)


#VRS Assumptions

VRS <- dea (X,Y, RTS = "vrs")
VRS

peers(VRS)
lambda(VRS)
dea.plot.frontier(X,Y,RTS="VRS")
summary(VRS, digits=4)

#IRS Assumptions

IRS <- dea (X,Y, RTS = "irs")
IRS

peers(IRS)
lambda(IRS)
dea.plot.frontier(X,Y,RTS="IRS")
summary(IRS, digits=4)

#DRS Assumptions 

DRS <- dea (X,Y, RTS = "drs")
VRS

peers(DRS)
lambda(DRS)
dea.plot.frontier(X,Y,RTS="DRS")
summary(DRS, digits=4)

#CRS Assumptions

CRS <- dea (X,Y, RTS = "crs")
CRS

peers(CRS)
lambda(CRS)
dea.plot.frontier(X,Y,RTS="CRS")
summary(CRS, digits=4)
```



#Express management’s objective function in terms of x1, x2, x3, y1+, y1- , y2+ and y2-. Formulate and solve the linear programming model. What are your findings? 
```{r}
library(lpSolve)
library(lpSolveAPI)
lprec <- read.lp("QMM Assignment #5.lp")
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
X <- "QMM Assignment #5.lp"
```
#Solving the lp, it can be found that 225 million is the maximum profit.


```{r}
library(lpSolve)
library(lpSolveAPI)
lprec <- read.lp("QMMnumber2.lp")
solve(lprec)
get.objective(lprec)
get.variables(lprec)
get.constraints(lprec)
Y <- "QMMnumber2.lp"
```

# The optimal solution is 208.333 for maximum profit. I that suggest the EMAX produces 0 from product 1, 8 from product 2, 3 from product 3. 

